Characterizing subarctic biomes for land surface modeling of ozone pollution and climate risk

### 2021-05-27 VegOzone.tex
Remove not used figures
Change title
Update affiliation

%\title{The 2018 heatwave and its implications on ozone induced damage on vegetation in a subarctic climate}
\title{Characterizing subarctic biomes for land surface modeling of pollution and climate risk}

@@

\affil[1]{Department of Geosciences, University of Oslo, Oslo, Norway}
\affil[2]{Department of Biosciences, University of Oslo, Oslo, Norway}
\affil[3]{Department of Environment and Geography, University of York, UK}

@@

%\begin{figure*}[t]
%  \includegraphics[width=12cm]{figA3}
%  \caption{Reconstruction of missing \chem{[O_3]} observation data at Svanvik in July 2018 based on derived hourly climatologies of northern Fennoscandia, Svanvik, and data Pallas. (a) Time series; (b) anomalies; (c) reconstruction.}
%  \label{fig:ozone_reconstruction_2018_07}
%\end{figure*}

>>>>

%\title{The 2018 heatwave and its implications on ozone induced damage on vegetation in a subarctic climate}
\title{Characterizing subarctic biomes for land surface modeling of ozone pollution and climate risk}

@@

\affil[1]{Department of Geosciences, University of Oslo, Oslo, Norway}
\affil[2]{Department of Biosciences, University of Oslo, Oslo, Norway}
\affil[3]{Department of Environment and Geography, Stockholm Environment Institute, University of York, UK}

@@
